Classless Java

### 2016-03-24 OOPSLA16/sections/CaseStudy.tex
fix

The last case study refactors the code from an interpreter for
a Lisp-like language
\lstinline{Mumbler}\footnote{https://github.com/cesquivias/mumbler/tree/master/simple},
which is created as a tutorial for the Truffle
Framework~\cite{wurthinger2013one}.  Keeping a balance between
simplicity and useful features, \lstinline{Mumbler} contains numbers,
booleans, lists (encoding function calls and special forms such as
if-expression, lambdas, etc). In the original code base, which
consists of 626 SLOC of Java, only one operation \texttt{eval} is
supported. Extending Mumbler to support one more operation, such as a
pretty printer, would normally require changing the existing code base
directly.

@@

\begin{tabular}{llll}
\hline
\rowcolor[HTML]{C0C0C0} 
Code               & SLOC & Code               & SLOC \\ \hline
old (eval)         & 626  & new (eval)         & 560  \\ 
\rowcolor[HTML]{C0C0C0}
old (eval + print) & 661  & new (eval + print) & 677  \\ \hline
\end{tabular}

>>>>

The last case study refactors the code from an interpreter for
a Lisp-like language
\lstinline{Mumbler}\footnote{https://github.com/cesquivias/mumbler/tree/master/simple},
which is created as a tutorial for the Truffle
Framework~\cite{wurthinger2013one}.  Keeping a balance between
simplicity and useful features, \lstinline{Mumbler} contains numbers,
booleans, lists (encoding function calls and special forms such as
if-expression, lambdas, etc). In the original code base, which
consists of 626 SLOC of Java, only one operation \texttt{eval} is
supported. Extending Mumbler to support one more operation, such as a
pretty printer \texttt{print}, would normally require changing the existing code base
directly.

@@

\vspace{0.5em}
\begin{tabular}{llll}
\hline
\rowcolor[HTML]{C0C0C0} 
Code               & SLOC & Code               & SLOC \\ \hline
old (\texttt{eval})         & 626  & new (\texttt{eval})         & 560  \\ 
\rowcolor[HTML]{C0C0C0}
old (\texttt{eval} + \texttt{print}) & 661  & new (\texttt{eval} + \texttt{print}) & 677  \\ \hline
\end{tabular}
